% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}

% Title
\title{PolitScanner Project Plan}
\author{Lena Merkli}

% Document
\begin{document}

    \maketitle
    \tableofcontents

    \bigskip\bigskip

    \section{Overview}\label{sec:overview}
    The AI system will analyze speeches by Swiss politicians to detect potential false narratives and fake news.
    It will not provide information about the accuracy in the speeches, rather it will provide factual information about the topics that were found in the speech.
    It has two inputs for this task: The written speech it is going to analyze and a list of false narratives and fake news.
    The output is a list of the false narratives and fake news that were found in the speech.
    To make it more specific, the speech will be split into parts with some overlap to not lose context, and these parts will be analyzed separately.
    Additionally, only a selection of the false narratives and fake news will be used as input, as determined by a text embedding model.

    \section{Database}\label{sec:database}
    The database will be kept intentionally small to ensure manageability while still demonstrating the concept's viability."
    One data point will consist of the following information:
    \begin{itemize}
        \item Topic summary
        \item Statements including fake news about the topic, both true and false
        \item The truth, based on scientific consensus
        \item A list of sources for the provided truth
    \end{itemize}

    \section{Vector Search}\label{sec:vector_search}
    The vector search will be based on embeddings of the database mentioned above.
    A standard run-of-the-mill vector search engine will be used for this task to do the first narrowing of the topics.

    \section{Part Splitting}\label{sec:part_splitting}
    The speech will be split into parts with some overlap to not lose context.
    For this, a simple transformer model will be trained and used.
    Text for the training data will be gathered from the official Swiss Parliament website.

    \section{Model}\label{sec:model}
    The model will be a fine-tuned version of a small and recent open-weight large language model.
    Unsloth on a RTX 4070 will be used for this task.

\end{document}
